---
title: "Interactive dashboards by Monisha"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
---

```{r,error=FALSE,warning=FALSE,message=FALSE}
library(plyr)
library(plotly)
library(ggplot2)
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(dplyr)
library(openintro)
library(highcharter)


# create some data
b <- read.csv("~/b.csv")
View(b)
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")
```

Overview
=======================================================================

Row
-----------------------------------------------------------------------
### Consumer Items Preference Analysis

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(paste("Global Statistics"),
         color = "warning")
```

### Total no.of.orders received during 2010-2016

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(length(b$Order.ID),
         icon = "fa-pencil")
```


### **Total Revenue**

```{r,error=FALSE,warning=FALSE,message=FALSE}
gauge(round(mean(b$Total.Revenue),
            digits = 6),
            min = 0,
            max = 10000000,
            gaugeSectors(danger = c(0, 250000),
                         warning = c(250000, 2500000),
                         success = c(2500000, 10000000),
                         colors = c("red", "yellow", "green")))
```

### times Europe tops as most demanded Region

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(sum(b$Region == "Europe"),
         icon = 'fa-tag')
```

### times Cuba tops as most demanded Country

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(sum(b$Country == "Cuba"),
         icon = 'fa-tag')
```


Row
-----------------------------------------------------------------------

### Time-Series of purchase orders according to Region
```{r,error=FALSE,warning=FALSE,message=FALSE}
p<-plot_ly(data=b,y=~Date,color=~Region,type='scatter',mode='lines')
p
```


Data Table
=======================================================================

Row
-----------------------------------------------------------------------


```{r,error=FALSE,warning=FALSE,message=FALSE}
datatable(b,
          caption = "Consumer Prefrence on Items",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```



Pivot Table
=========================================

```{r,error=FALSE,warning=FALSE,message=FALSE}
rpivotTable(b,
            aggregatorName = "Count",
            cols= "Unit.Price",
            rows = "Region",
            rendererName = "Heatmap")
```


Demand
=======================================================================

Row
-----------------------------------------------------------------------

### The most sellable items are in Europe region!!

```{r,error=FALSE,warning=FALSE,message=FALSE}
x<-c('Baby Food','Beverages','Cereal','Clothes','Cosmetics','Fruits','Household','Meat','Office Supplies','Personal Care','Snacks','Vegetables')
y<-c(24,28,19,22,19,14,25,12,26,23,25,30)
data <- data.frame(x,y)
a<-ggplot(data,aes(x=x,y=y,ymin=12,ymax=30))+geom_pointrange(color="blue",size=2)+theme(axis.text.x = element_text(angle=45,hjust=1))
ggplotly(a)


```


### Which item has highest demand in market?

```{r,error=FALSE,warning=FALSE,message=FALSE}

b %>% plot_ly(labels = ~Item.Type, values = ~Units.Sold) %>% add_pie(hole = 0.6)

```

Row
-----------------------------------------------------------------------

### Which item profited the sales in the market according to priority ?

```{r,error=FALSE,warning=FALSE,message=FALSE}
 p <- plot_ly(b, x = ~Item.Type, y = ~Total.Profit, color = ~Order.Priority, type = "box") %>%
  layout(boxmode = "group")
p
 
```

### The disturibution of Total Revenue,Total Cost and Total Profit

`
```{r,error=FALSE,warning=FALSE,message=FALSE}
x<-c("TotalRevenue","TotalCost","TotalProfit")
y<-c(132,93,39)
data<-data.frame(x,y)
plot_ly(data,x=~x,y=~y,type='bar',marker=list(color=c('rgba(204,204,204,1)','rgba(204,204,204,1)', 'rgba(222,45,38,0.8)'))) %>% layout(yaxis=list(title="Measured in crores"))
```

Supply
=======================================================================

Row
-----------------------------------------------------------------------

### How Cost and Price varied during selling of Item?

```{r,error=FALSE,warning=FALSE,message=FALSE}

x<-c('Baby Food','Beverages','Cereal','Clothes','Cosmetics','Fruits','Household','Meat','Office Supplies','Personal Care','Snacks','Vegetables')
z<-c(255.28,47.45,205.7,109.28,437.2,9.33,668.27,421.89,651.21,81.73,152.58,154.06)
y<-c(159.42,31.79,117.11,35.84,263.33,6.92,502.54,364.69,524.96,56.67,97.44,90.93)
data <- data.frame(x,y,z)
data$x <- factor(data$x, levels = data[["x"]])
p <- plot_ly(data, x = ~x, y = ~y, type = 'bar', name = 'Unit Cost', marker = list(color = 'rgb(49,130,189)')) %>% add_trace(y = ~z, name = 'Unit Price', marker = list(color = 'rgb(204,204,204)')) %>%layout(xaxis = list(title = "", tickangle = -45),yaxis = list(title = ""),margin = list(b = 100),barmode = 'group')
p
```

### How the difference in Cost and Price increased Profits in market share?

```{r,error=FALSE,warning=FALSE,message=FALSE}
pal<-c("grey","grey","yellow","green","yellow","grey","grey","red","grey","grey","grey","yellow")
s<-plot_ly(data=b,x=b$Item.Type,y=((b$Unit.Price-b$Unit.Cost)/b$Unit.Price)*100,type='scatter',color=~Item.Type,colors=pal)
s
```

Row
-----------------------------------------------------------------------

### Units Sold according to Items

```{r,error=FALSE,warning=FALSE,message=FALSE}
plot_ly(b,x=~Item.Type,y=~Units.Sold,type='violin',split=~Item.Type,box=list(visible=T),mean=list(visible=T))
```

### The most sellable items are in Cuba country!!!?

```{r}
y<- c(1,1,2,1,2,1,2,1) 
x<-c('Beverages','Cereal','Clothes','Cosmetics','Household','Meat','Office Supplies','Personal Care')
data <- data.frame(x,y)
 plot_ly(data, labels = ~x, values =~y) %>% add_pie(hole=0.6)

```


Summary {data-orientation=columns} 
===========================================

Column 
-----------------------------------

### Max Unit Price

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(max(b$Unit.Price),
         icon = "fa-random" )
```

### Max Unit Cost

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(max(b$Unit.Cost),
         icon = "fa-random" )
```

### Average Items Pricing 
```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(round(mean(b$Unit.Price),
               digits = 3),
         icon = "fa-thumbs-up")
```

### Average Items Sold 

```{r,error=FALSE,warning=FALSE,message=FALSE}
valueBox(round(mean(b$Units.Sold), digits = 4),
         icon = "fa-thumbs-up")
```

Column
---------------------------

Report

* This is a report for 1000 Items analysed.
* Created by<b> Monisha Anila</b> on Consumer Preference Items Analysis. 
* <b>Europe</b>'s one of the most sellable `Beverages` gives strong confidence on demand in market.
* When coming to the overall profit `Beverages` is less than `Meat` considering <b>Europe</b>'s statistics.
* When varying cost and price of the items `Households` hold the highest spot but in profits `Clothes` tops the list.
* The profited item `Clothes` tops the most sellable item in <b>Cuba</b>. Making significant important item not only in <b>Cuba</b> but to the entire world.
* This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.
